% Andrew Faust's Resume
% URL: 
%
% Based on resume tex file by Kamil Wojcicki
% URL: http://linux.dsplabs.com.au/resume-writing-example-latex-template-linux-curriculum-vitae-professional-cv-layout-format-text-p54/

\documentclass[margin,line,11pt]{resume}

\usepackage{graphicx}

\begin{document}

\name{\Huge Andrew Faust}
{
	\sc
    \hfill (310) 465-7170           \vspace{0mm}\\\vspace{0mm}%
    \hfill andrewjfaust@gmail.com   \vspace{0mm}\\\vspace{0mm}%
    \hfill linkedin.com/in/ajfaust  \vspace{0mm}\\\vspace{0mm}%
}

\begin{resume}

\vspace{1mm}

    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle \textbf{\large{S}\small{KILLS}}}

    \textbf{Languages:}\hspace{2mm}C\#,\hspace{2mm}SQL,\hspace{2mm}Python,\hspace{2mm}HTML/CSS/JavaScript,\hspace{2mm}C++,\hspace{2mm}C\\
    \textbf{Technologies:}\hspace{2mm}.NET,\hspace{2mm}ASP.NET,\hspace{2mm}Git,\hspace{2mm}Azure,\hspace{2mm}CI/CD, Docker\\
    \textbf{Environments:}\hspace{2mm}Visual Studio,\hspace{2mm}Microsoft SSMS,\hspace{2mm}Microsoft Power BI.
\sectionline

    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle \textbf{\large{P}\small{ROFESSIONAL\\EXPERIENCE}}}

    % Zoox Engineering Manager
    \textbf{\listing ZPower LLC}, Camarillo, CA \vspace{2mm}\\\vspace{1mm}
    \textsl{Software Engineer} \hfill \textbf{Jan 2018 -- Present}\\
    \begin{list2}
        \item Developed a desktop application using C\# and .NET Core used to sort battery cells after testing by communicating with a sorter machine and SQL databases.
        \item Overhauled a desktop application used to determine battery quality via a third-party vision software. Improves upon the previous UI and adds SQL data storage, greatly increasing data retrieval and analysis.
        \item Implemented CI/CD pipelines using Azure DevOps, greatly increasing efficiency of deployments and build validations.
        \item Produced key performance business intelligence reports, allowing multiple departments to visually assess crucial production data such as throughput, revenue, and quality in close to real time.
        \item Developed internal web pages using ASP.NET for employees to visualize production data across all stages of the production process and create records of other critical data such as failure analysis and quality control.
    \end{list2}

    \textbf{\listing Bunim/Murray Productions}, Glendale, CA \vspace{2mm}\\\vspace{1mm}
    \textsl{Contract Software Developer} \hfill \textbf{Sep 2017 -- Nov 2017}\\
    \begin{list2}
        \item Utilized REST and SOAP APIs to create scripts to transfer employee data from UltiPro HCM to on-premise storage. Increased efficiency for HR by allowing for automated form completion.
        \item Recreated a call log application used by the CEO by creating a similar UI using FileMaker Pro and backfilling data from an old Microsoft SQL database into an on-premise database.
    \end{list2}
    

\sectionline

    \section{\mysidestyle \textbf{\large{P}\small{ROJECTS}}}
    \textbf{\listing Thread Library} \hfill \textbf{May 2017}\\
    \begin{list2}
        \item Created a user-level thread library in C that allows users to create and manage multiple threads. Implements thread preemption, semaphore locks, and thread private storage. A linked-list queue library was also created to keep track of running threads.
    \end{list2}

    \textbf{\listing IEEE 802.11-Based WLAN Simulation} \hfill \textbf{March 2017}\\
    \begin{list2}
        \item Developed a time-based Discrete Event Simulation of an ad-hoc WLAN network in Python between 20 hosts, using an exponential backoff scheme and a doubly-linked list acting as a global event list.
    \end{list2}

\sectionline

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle \textbf{\large{E}\small{DUCATION}}}

    \textbf{\listing University of California, Davis}, Davis, California \vspace{2mm}\\\vspace{1mm}%
    \textsl{B.S. of Computer Science} \hfill \textbf{ Sep 2015 -- June 2017}\vspace{-3mm}\\\vspace{-1mm}%


\end{resume}
\end{document}
